---
title: "Assignment Six"
author: "Suprit Saha"
date: "Sunday, April 05, 2015"
output: html_document
---

**Question 1**

Create user defined function/functions 
User can input any data
The result will be two datasets :

* One having quantitative variables
* Other having categorical/character variables
* Use stat.desc to get descriptive statistics of quantitative variables
* Use summary to get descriptive statistics of quantitative variables

```{r}
DataNumeric <- function(dataset)
{ 
  dataNum <- dataset[,sapply(dataset, function(x) is.numeric(x) | is.integer(x))]
  return(dataNum)
}

DatanonNumeric <- function(dataset)
{ 
  datanonNum <- dataset[,sapply(dataset, function(x) is.character(x) | is.factor(x) | is.logical(x))]
  return(datanonNum)
}
```

We have created two user defined functions.Let us see the output by calling the functions
```{r}
custdata <- read.table(file = "C:\\Users\\Suprit\\Desktop\\Anaken R\\Tutorial Eight\\CustomerData.txt",header = TRUE,sep = "\t",na.strings = c("",NA))

head(DataNumeric(dataset = custdata))
head(DatanonNumeric(dataset = custdata))

```

